A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-25 rmtw/a4/latex8.tex
feedback a4

\subsection{Results for H\textsubscript{Eff} and H\textsubscript{Rate}}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was performed instead of the Student's T-test as the test for H\textsubscript{Eff}. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was p=0.1063 and thus the alternative hypothesis, H\textsubscript{1 Eff}, is rejected.

The same test was chosen for H\textsubscript{Rate}, based on the same reasoning. The result of the WMW test for H\textsubscript{Rate} was p=0.1063 and thus H\textsubscript{1 Rate} is rejected.

As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar. Both show that there is a slight difference between the two inspection methods, and there is a slight better result for CL. The results are, however, not statistically significant enough for the null hypotheses to be rejected. Table 3 shows that UC finds more faults of risk type A and C, but the fact that the CL data contained 18 more faults that contained an incorrect fault risk entry is be a possible explanation for this result.

\subsection{Results for H\textsubscript{Fault}}
As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results. The result of the $\chi $ \textsuperscript{2} was 1.5998, generating a p-value of 0.4494. For $\nu$=2 and $\alpha$=0.05, the upper critical value is 5.991 and the lower critical value is 0.103. Since 1.5998 is \textless 5.991 and \textgreater 0.103, the alternative hypothesis of the CS test is rejected. Since H\textsubscript{0 Fault} and H\textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.

>>>>

\subsection{Results for H\textsubscript{Eff} and H\textsubscript{Rate}}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was performed instead of the Student's T-test as the test for H\textsubscript{Eff}. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was p=0.1063 and thus the results are not statistically significant enough to reject the null hypothesis.

The same test was chosen for H\textsubscript{Rate}, based on the same reasoning. The result of the WMW test for H\textsubscript{Rate} was p=0.1063 and thus the results are not statistically significant enough to reject H\textsubscript{0 Rate}.

As is evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar. Both show that there is a slight difference between the two inspection methods, and there is a slightly better result for CL. The results are, however, not statistically significant enough for the null hypotheses to be rejected. Table 3 shows that UC finds more faults of risk type A and C, but the fact that the CL data contained 18 more faults that contained an incorrect fault risk entry is be a possible explanation for this result.

\subsection{Results for H\textsubscript{Fault}}
As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results. The result of the $\chi $ \textsuperscript{2} was 1.5998, generating a p-value of 0.4494. For $\nu$=2 and $\alpha$=0.05, the upper critical value is 5.991 and the lower critical value is 0.103. Since 1.5998 is \textless 5.991 and \textgreater 0.103, the results are not statistically significant enough for the null hypothesis to be rejected.
